% COMPOSITE

\subsection{Quiz}

\subsubsection{Question 1}

\vspace{1em}

\begin{solution}
	Since there are no velocity vectors, it is impossible to determine whether or not the particle is slowing down or speeding up.
\end{solution}

\subsubsection{Question 2}

\vspace{1em}

\begin{solution}
	The object is moving downwards, but decreasing in speed. This means that the acceleration vector is opposite of the velocity vector, which (in this case) means that $a_y$ is pointing upwards.
\end{solution}

\subsubsection{Question 3}

\vspace{1em}

\begin{solution}
	The sign of the position, velocity, and acceleration are all positive, since the object is above the $y$-axis and is accelerating upwards (increasing in speed)
\end{solution}

\subsubsection{Question 4}

\vspace{1em}

\begin{solution}
	Since the direction of the particle was not specified, I chose for the velocity vectors to point to the right. The acceleration vectors initially would be opposite of the velocity vectors (since the object was slowing down), but after point 2 the acceleration would be in the same direction as the velocity.
\end{solution}

\subsubsection{Question 5}

\vspace{1em}

\begin{solution}
	I chose the first motion diagram, since the acceleration vectors and velocity vectors align with the problem most accurately.
\end{solution}

\subsubsection{Question 6}

\vspace{1em}

\begin{solution}
	I chose option 3, since Eustace would need to drive back in the same direction away from El Dorado.
\end{solution}

\subsubsection{Question 7}

\vspace{1em}

\begin{solution}
	\begin{enumerate}[label=\Alph*.]
		\item $8.181 \times 10^{-1} \to$ 4 significant figures
		\item $95.0 \to$ 3 significant figures (trailing zero after decimal is significant)
		\item $0.0469 \to$ 3 significant figures
		\item $0.04 \times 10^{8} \to$ 1 significant figure
	\end{enumerate}
\end{solution}

\subsubsection{Question 8}

\vspace{1em}

\begin{solution}
	\begin{enumerate}[label=\Alph*.]
		\item $159.31 \cdot 204.6 = 32594.826 \approx 32590$
		\item $5.1125 + 0.67 + 3.2 = 8.9825 \approx 9.0$
		\item $7.662 - 7.425 = 0.237$
		\item $\frac{16.5}{3.45} = 4.7826087 \approx 4.78$
	\end{enumerate}
\end{solution}

\subsubsection{Question 9}

\vspace{1em}

\begin{solution}
	\begin{enumerate}[label=\Alph*.]
		\item I chose the fourth motion diagram since the acceleration vectors are pointing in the appropriate direction.
		\item I chose the fourth word description because cyclist $B$ would need to be travelling slower in order for them to meet.
		\item I chose the first pictoral because it aligns with the problem most accurately (the accelerations are correct)
	\end{enumerate}
\end{solution}

\subsubsection{Question 10}

\vspace{1em}

\begin{solution}
	\begin{enumerate}[label=\Alph*.]
		\item $81 \text{in} \cdot 0.0254 \text{m/in} = 2.0574 \text{m}$
		\item $4.45 \cdot 10^{6} \text{yr} \cdot 3.154 \cdot 10^{7} \text{s/yr} = 1.404 \cdot 10^{14} \text{s}$
		\item $69 \text{ft/day} \cdot \frac{0.3048\text{m}}{1\text{ft}} \cdot \frac{1}{86400\text{s/day}} = 2.434 \cdot 10^{-4}\text{m/s}$ 
		\item $3.2 \cdot 10^{4}\text{mi}^2 \cdot 2.58999 \cdot 10^{6} \text{m}^2\text{mi}^2 = 8.288 \cdot 10^{10} \text{m}^2$
	\end{enumerate}
\end{solution}

\subsubsection{Question 11}

\vspace{1em}

\begin{solution}
	\begin{align*}
		\text{time} &= \frac{\text{distance}}{\text{speed}} \\
		\text{time} &= \frac{0.8\text{m}}{25\text{m/s}} \\
		&= 0.032~\text{seconds} \\
		&\approx 30~\text{ms}
	.\end{align*}
\end{solution}

\subsubsection{Question 12}

\vspace{1em}

\begin{solution}
	\begin{align*}
		7.5\text{g/L} &= 7.5 \cdot 0.001 \text{kg/L} = 0.0075 \text{kg/L} \\
		1\text{L} &= 0.001\text{m}^3 \\
		0.0075\text{kg/L} \cdot \frac{1}{0.001\text{m}^3\text{/L}} &= 7.5\text{kg/m}^3
	.\end{align*}
\end{solution}
